Supporting information: Copulas and their potential for ecology

### 2019-12-18 AER_Responses.tex
changed distribution function to cdf

>>>

@@

Review of Ghosh et al.: Copulas and the Potential for Ecology
I would like to thank the authors for their manuscript entitled "Copulas and their potential for ecology".  The manuscript provides an introduction to the concept of copulas and their utility for application in studying the natures of variable dependency in ecology.  The authors demonstrate that the most commonly used models of inference, correlation and regression, only encapsulate certain features of the dependency between variables and the author introduce a more complete method of inference to an ecologist audience.
I must first state that I must give fair warning that, whilst I have heard about copulas before, I have never applied them to my own research and I certainly cannot claim to be an expert in this area.  I am therefore probably the target audience of this paper.  This means that whilst I can give constructive feedback on the author's introduction of the concepts to an ecologist readership and can follow the mathematical background that they have provided, I cannot necessarily state definitively whether the authors have reproduced a fair portrayal of the theory of copulas in this manuscript.
However, despite not being a specialist on the subject, I found the presentation of the manuscript reasonably easy to follow and the authors should be commended for making what is quite a dense subject approachable.  Each theoretical claim is backed by well-documented supplementary materials which allows for digestion of the key concepts without being side-tracked by dense mathematical derivations.

@@

>>><DAN: to add some discussion material>

@@

What follows is a small set of very minor points that are all highly subjective and whether or not they are addressed does not, in my view, preclude the manuscript of being published:
o    The authors use the term "distribution function" to represent "cumulative distribution function".  My feeling is that ecologists in general are more familiar with the term "cumulative distribution function" (which thereafter can be abbreviated to "CDF") as the former is more likely to be mistaken for the density function.

@@

o    The manuscript could benefit from a little more detail in the introduction as to how this material goes further than that in other ecological introductions to copulas.  For example, Anderson et al. 2018 also contains an introduction to the theory of copulas so if might be worth explicitly pointing out how this paper goes further in explaining and introducing the concept to an ecologist audience.

o    A table giving a run-down of the notation used in the manuscript might be useful for the more mathematically-adverse reader.  A sort of notation cheat-sheet for easy notation lookup would be useful for readers so that they can concentrate on the new concepts rather than looking up notation definitions.

@@

o    The authors make reference to many families of copula models (a total of 16 families) and, whilst there is a graphical illustration of the shapes of the copulas, we don't see the functional forms of these copulas.  A table either in the main text or supplementary materials giving these would be appreciated.

>>><Shyamolina is collecting the formulas>

>>>>

>>><***DAN to fill in>

@@

Review of Ghosh et al.: Copulas and the Potential for Ecology
I would like to thank the authors for their manuscript entitled "Copulas and their potential 
for ecology".  The manuscript provides an introduction to the concept of copulas and their 
utility for application in studying the natures of variable dependency in ecology.  The 
authors demonstrate that the most commonly used models of inference, correlation and regression, 
only encapsulate certain features of the dependency between variables and the author introduce a 
more complete method of inference to an ecologist audience.

I must first state that I must give fair warning that, whilst I have heard about copulas before, 
I have never applied them to my own research and I certainly cannot claim to be an expert in this 
area.  I am therefore probably the target audience of this paper.  This means that whilst I can 
give constructive feedback on the author's introduction of the concepts to an ecologist readership 
and can follow the mathematical background that they have provided, I cannot necessarily state 
definitively whether the authors have reproduced a fair portrayal of the theory of copulas in this 
manuscript.

However, despite not being a specialist on the subject, I found the presentation of the manuscript 
reasonably easy to follow and the authors should be commended for making what is quite a dense 
subject approachable.

>>>Many thanks for the positive feedback! We worked hard for clarity.

Each theoretical claim is backed by well-documented supplementary materials which allows for 
digestion of the key concepts without being side-tracked by dense mathematical derivations.

@@

>>>We have added a paragraph to the Discussion on this topic. Whereas certainly 
one could use the approach of regression models with heteroskedastic error variance to 
explore tail associations, probably gaining insight, copulas have theoretical 
and practical advantages sketched in the new paragraph.

@@

What follows is a small set of very minor points that are all highly subjective and whether 
or not they are addressed does not, in my view, preclude the manuscript of being published:

>>>Thank you for giving us some reasonable wiggle room here, which helps in light of 
other constraints.

The authors use the term "distribution function" to represent "cumulative distribution 
function".  My feeling is that ecologists in general are more familiar with the term 
"cumulative distribution function" (which thereafter can be abbreviated to "CDF") as the 
former is more likely to be mistaken for the density function.

>>>We made the change as requested, thanks for the suggestion.

The manuscript could benefit from a little more detail in the introduction as to how 
this material goes further than that in other ecological introductions to copulas.  
For example, Anderson et al. 2018 also contains an introduction to the theory of copulas 
so if might be worth explicitly pointing out how this paper goes further in explaining 
and introducing the concept to an ecologist audience.

@@

A table giving a run-down of the notation used in the manuscript might be useful for the 
more mathematically-adverse reader.  A sort of notation cheat-sheet for easy notation 
lookup would be useful for readers so that they can concentrate on the new concepts rather 
than looking up notation definitions.

@@

The authors make reference to many families of copula models (a total of 16 families) and, 
whilst there is a graphical illustration of the shapes of the copulas, we don't see the 
functional forms of these copulas.  A table either in the main text or supplementary materials 
giving these would be appreciated.

>>>Thank you for this suggestion. Exactly such a table was already provided by Brechmann 
and Schepsmeier (2013, Journal of Statistical Software), so rather than reproduce it, we
now include a reference to that work. We also feel like such a table would alienate most
of the audience we are trying to reach here. In fact we have not found the formulas
for the copula families to be particularly useful knowledge for standard ecological 
application (though they will be intimidating to some readers). Rather, it helps to 
know the properties of the copula families (which we describe) and what they look 
like (which we show). Of course mathematical applications will need the formulas, but 
I think most readers will be quantitative ecologists who want to use these families 
but, in our estimation based on our experience of using the families ourselves, will 
have almost no occassion to use the formulas.
